Verifying Demonstrations

### 2018-03-16 paper/protocol.tex
Converts paper to IEEEtran
Smaller font size in protocol and proofshare figures
Fixes fontsizes in protocol figures
Writes up setup and registration

\NewCryptoScheme{\PRIVOscheme}{PRIVO}
\NewAlgorithm{\PRIVOsetup}{\PRIVOscheme.\!Setup}
\NewAlgorithm{\PRIVOreg}{\PRIVOscheme.\!Register}
\NewAlgorithm{\PRIVOjoin}{\PRIVOscheme.\!Join}
\NewAlgorithm{\PRIVOparticipate}{\PRIVOscheme.\!Participate}
\NewAlgorithm{\PRIVOsubmit}{\PRIVOscheme.\!Submit}

@@

\emph{Setup: \((spk, ssk)\gets \PRIVOsetup\).}
The setup phase is for the \ac{CA} to set up all the needed keys.
The \ac{CA} starts by generating a service public-private key-pair \((spk, 
  ssk)\) by the following.
\(\gets \PRIVOsetup[1^\lambda]\), where \(\lambda\) is the security parameter, 
and then publishes \(spk\).
\begin{algorithmic}
  \Function{\PRIVOsetup}{$1^\lambda$}
    \State{$spk\gets (g, G, q, \dots)$}
    \State{$ssk\gets (g, G, q, \dots)$}
    \State{\Return{$(spk, ssk)$}}
  \EndFunction
\end{algorithmic}

@@

\begin{figure}
  \centering
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protester \(P\)'s identifier \(pid\) is computed using the protester's 
    key \(k_P\).
    The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
    \(k_W\).
    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
    The protest (cause) identifier \(cid\) is the hash value of the manifesto.
  }%
  \label{fig:ProofFig}
\end{figure}%

\begin{figure}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & cid\gets \Hash[\text{manifesto}], \\
        & pid\gets \ACprf[_{k_P}][cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill\small Join}
      \midrule
      \noalign{\hfill\small Participation}
      \\[-3em]
      P\to W\colon & pid \\
      P\leftrightarrow W\colon &
        \DBPK\mleft\{ (k_P) : \mright. \\
        & \qquad pid = \ACprf[_{k_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
      W\colon & wid\gets \ACprf[_{k_W}][pid], \\
        & wsig\gets \ACprf[_{k_W}][wid, t_s, t_s', l] \\
      W\to P\colon & (wid, t_s, t_s', l, wsig)
      \\[-1em]
      \noalign{\hfill\small Participation}
      \midrule
      \noalign{\hfill\small Submission}
      \\[-2em]
      W\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      P\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_W),\quad 
      \text{where} \\
        & \pi_W = \SPK\mleft\{ (k_W) : \mright. \\
        & \qquad wid = \ACprf[_{k_W}][pid], \\
        & \qquad wsig = \ACprf[_{k_W}][wid, t_s, t_s', l], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{ssk}][k_W]]\mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig) \\
      P\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_P),\quad 
      \text{where}\\
        & \pi_P = \SPK\mleft\{ (k_P) : \mright. \\
        & \qquad pid = \ACprf[_{k_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}

>>>>

\NewCryptoScheme{\PRIVOscheme}{PRIVO}
\NewAlgorithm{\PRIVOsetup}{Setup}
\NewAlgorithm{\PRIVOreg}{Register}
\NewAlgorithm{\PRIVOjoin}{Join}
\NewAlgorithm{\PRIVOparticipate}{Participate}
\NewAlgorithm{\PRIVOsubmit}{Submit}

@@

The setup and registration phases are the same as in Anon-Pass~\cite{AnonPass}.
We have simply adapted their description for our notation, but tried to keep 
them as similar as possible.

\emph{Setup: \((spk, ssk)\gets \PRIVOsetup\).}
The setup phase is for the \ac{CA} to set up all the needed keys.
The \ac{CA} generates a service public-private key-pair \((spk, ssk)\) as 
follows.
Let \(G = \gen g\) be a group with generator \(g\) and prime order \(q\).
Let \(G_T\) be a group such that there is a bilinear pairing \(e\colon G\times 
  G\to G_T\)\footnote{%
  \Ie \(e(g_1^a, g_2^b) = e(g_1, g_2)^{ab}\) and if \(G = \gen{g_1} = 
    \gen{g_2}\) then \(G_T = \gen{e(g_1, g_2)}\).
}.
Choose \(x,y,z\rgets \ZZ_q\) uniformly at random and set \(X = g^x, Y = g^y, Z = 
  g^z\).
Then the service public key \(spk = (q, G, G_T, g, X, Y, Z)\) and the service 
private key \(ssk = (x, y, z)\).

\emph{Registration: \(sk\gets 
    \Proto{\PRIVOreg[_P][spk]}{\PRIVOreg[_{CA}][ssk]}\).}
During the registration phase, each protester will generate a secret key and 
obtain a signature on it by the \ac{CA} --- without revealing it to the \ac{CA}.
Thus each protester will have a signed secret key, the \ac{CA} will issue only 
one signature per protester but will not know who has which key.
The protester chooses \(d, r\gets \ZZ_q\) uniformly randomly and sets \(M = g^d 
  Z^r\) and send \(M\) to the server.
The protester acts as prover and the \ac{CA} as verifier while they perform the 
following \ac{ZKPK} protocol: \(\PK[d,r][M = g^d Z^r]\).
If the proof succeeds, the \ac{CA} chooses \(a\gets \ZZ_q^*\) and sets \(A = 
  g^a\).
Then it forms the signature \(s = (A, B = A^y, Z_B = B^z = Z^{ay}, C = A^x 
  M^{axy})\) and sends it to the protester.
The protester verifies that the following equations hold:
\begin{align*}
  A &\neq 1 \\
  e(g, B) &= e(Y, A) \\
  e(g, Z_B) &= e(Z, B) \\
  e(g, C) &= e(X, A) e(X, B)^d e(X, Z_B)^r.
\end{align*}
Upon success, the protester uses \(sk = (s, d, r)\).

The setup and registration phases can be done once and the keys reused for an 
arbitrary number of protests.
Thus it would be suitable to have the registration phase as part of the issuance 
of \eg national identity cards, passports or \acp{eID}.

\subsection{Old}

@@

\begin{figure}
  \centering
  \footnotesize
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protester \(P\)'s identifier \(pid\) is computed using the protester's 
    key \(k_P\).
    The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
    \(k_W\).
    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
    The protest (cause) identifier \(cid\) is the hash value of the manifesto.
  }%
  \label{fig:ProofFig}
\end{figure}%

\begin{figure}
  \centering
  \footnotesize
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & cid\gets \Hash[\text{manifesto}], \\
        & pid\gets \ACprf[_{k_P}][cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & pid \\
      P\leftrightarrow W\colon &
        \DBPK\mleft\{ (k_P) : \mright. \\
        & \qquad pid = \ACprf[_{k_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
      W\colon & wid\gets \ACprf[_{k_W}][pid], \\
        & wsig\gets \ACprf[_{k_W}][wid, t_s, t_s', l] \\
      W\to P\colon & (wid, t_s, t_s', l, wsig)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      W\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      P\colon & t_e\gets \TSstamp[\Hash[pid, wid, t_s, t_s', l, wsig]] \\
      W\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_W),\quad 
      \text{where} \\
        & \pi_W = \SPK\mleft\{ (k_W) : \mright. \\
        & \qquad wid = \ACprf[_{k_W}][pid], \\
        & \qquad wsig = \ACprf[_{k_W}][wid, t_s, t_s', l], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{ssk}][k_W]]\mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig) \\
      P\to S\colon & (pid, wid, t_s, t_s', t_e, l, wsig, \pi_P),\quad 
      \text{where}\\
        & \pi_P = \SPK\mleft\{ (k_P) : \mright. \\
        & \qquad pid = \ACprf[_{k_P}][cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{ssk}][k_P]] \mright\} \\
        & \qquad\qquad (pid, wid, t_s, t_s', l, wsig)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}
